---
title: "Ex2"
author: "Yahav"
date: "2022-11-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Exercise 2

## Question 1

We can use the binomial distribution to calculate the probability that a family with 4 children
has 2 girls and 2 boys.

In our case $p = 0.49$ (the probability to conceive a girl), $n = 4$ (there are 4 independent pregnancies)
and $x = 2$ (we want exactly 2 girls and the rest - 2 will be boys).

Let's calculate the final result:

```{r}
dbinom(x=2, size=4, prob=0.49)
```



## Question 2

We can use again the binomial distribution, but in this case $n = 10$ (there are 10 children) and $x = 6$
(we want exactly 6 girls and the rest - 4 will be boys).

Let's calculate the final result:

```{r}
dbinom(x=6, size=10, prob=0.49)
```



## Question 3


```{r}
x = seq(1, 50, 1)
lambda_1 = 1
lambda_2 = 10
lambda_3 = 30

pois_1 = dpois(x, lambda=lambda_1)
pois_10 = dpois(x, lambda=lambda_2)
pois_30 = dpois(x, lambda=lambda_3)

range = 0:49

plot(range, pois_1)
plot(range, pois_10)
plot(range, pois_30)
```
