---
title: "Ex1"
author: "Yahav"
date: "2022-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Exercises

## Computations in R

#### Exercise 1

```{r}
2 + 3
```

#### Exercise 2

```{r}
sqrt(36)
```

#### Exercise 3

```{r}
log10(1000)
```

#### Exercise 4

```{r}
log2(32)
```

#### Exercise 5

```{r}
x = 2 + 3 + 4
```

#### Exercise 6

```{r}
abs(5 - 145)
```

#### Exercise 7

```{r}
x = sqrt(625) / 5
print(x)
```

#### Exercise 8

```{r}
x = x * 10000
print(x)
```

## Data structures in R

#### Exercise 10

```{r}
vec = c(1, 2, 3, 5, 10)
```

#### Exercise 11

```{r}
length(vec)
```

#### Exercise 12

```{r}
2:15
```

#### Exercise 13

```{r}
rep(x=4, times=5)
```

#### Exercise 14

```{r}
c(TRUE, TRUE, FALSE, FALSE)
```

#### Exercise 15

```{r}
vec = c(c("P", "A", "X", "6"), c("Z", "I", "C", "2"), c("O", "C", "T", "4"), c("S", "O", "X", "2"))
print(vec)
```

#### Exercise 16

```{r}
vec[5:6]
```

#### Exercise 17

```{r}
myvec = 1:5
myvec[c(TRUE,TRUE,FALSE,FALSE,FALSE)]
myvec[c(TRUE,FALSE,FALSE,FALSE,TRUE)]
```

#### Exercise 18

```{r}
myvec > 3
myvec == 4
myvec <= 2
myvec != 4
```

#### Exercise 19

```{r}
myvec[myvec > 2]
```

#### Exercise 20

```{r}
matrix(1:15, nrow=5, ncol=3)
```

#### Exercise 21

```{r}
mat = matrix(1:15, nrow=5, ncol=3, byrow=TRUE)
```

#### Exercise 22

```{r}
mat[1:3, 1:3]
```

#### Exercise 23

```{r}
mat[2:3,]
```

#### Exercise 24

```{r}
class(mat[,1:2])
```

#### Exercise 25

```{r}
class(mat[,1])
```

#### Exercise 26

```{r}
df = data.frame(col1=1:5, col2=c("a", "b", "c", "d", "e"), col3=10:14)
```

#### Exercise 27

```{r}
df[1:2, 1:2]
```

#### Exercise 28

```{r}
df[2:3,]
```

#### Exercise 29

```{r}
df[,c("col2", "col3")]
```

#### Exercise 30

```{r}
df$col2
```

#### Exercise 31

```{r}
df[which(df[, "col1"] > 3),]
df[df$col1 > 3,]
```

#### Exercise 32

```{r}
df[which(df[, "col1"] >= 3),]
df[df$col1 >= 3,]
```

#### Exercise 33

```{r}
as.matrix(df)
```

#### Exercise 34

```{r}
mylist = list(a=c("1", "2", "3"), b=5, c=1, d=7)
```

#### Exercise 35

```{r}
mylist$a
```

#### Exercise 36

```{r}
mylist$d
```

#### Exercise 37

```{r}
mylist[1]
```

#### Exercise 38

```{r}
mylist[4]
```

#### Exercise 39

```{r}
fa = factor(c("a", "b", "c", "d", "e"))
fa
```

#### Exercise 40

```{r}
vec = c("a", "b", "c", "d", "e")
fa = as.factor(vec)
print(fa)
```

#### Exercise 41

```{r}
as.character(fa)
```



## Reading in and writing data out in R

#### Exercise 1

```{r}
cpgFilePath = system.file("extdata", "CpGi.table.hg18.txt", package="compGenomRData")
cpgData = read.delim(cpgFilePath)
```

#### Exercise 2

```{r}
head(cpgData)
```

#### Exercise 3

```{r}
cpgtFilePath=system.file("extdata", "CpGi.table.hg18.txt", package="compGenomRData")

cpgiSepComma=read.table(cpgtFilePath, header=TRUE, sep=",")
head(cpgiSepComma)
```

#### Exercise 4

```{r}
cpgtFilePath=system.file("extdata", "CpGi.table.hg18.txt", package="compGenomRData")

cpgiHF=read.table(cpgtFilePath, header=FALSE, sep="\t", stringsAsFactors=FALSE)
head(cpgiSepComma)
```

#### Exercise 5

```{r}
cpgiSepComma[1:10,]
```

#### Exercise 6

```{r}
head(read.table(cpgFilePath, header=FALSE, sep="\t"))
```

#### Exercise 7

```{r}
write.table(cpgData, file="C:/Users/Yahav/Desktop/my.cpgi.file.txt")
```

#### Exercise 8

```{r}
write.table(cpgData, file="C:/Users/Yahav/Desktop/my.cpgi.file2.txt", quote=FALSE, sep="\t", row.names=FALSE)
```

#### Exercise 9

```{r}
write.table(cpgData[1:10,], file="C:/Users/Yahav/Desktop/my.cpgi.file3.txt")
```

#### Exercise 10

```{r}
write.table(cpgData[,1:3], file="C:/Users/Yahav/Desktop/my.cpgi.file4.txt")
```

#### Exercise 11

```{r}
write.table(cpgData[cpgData$chrom == "chr1",], file="C:/Users/Yahav/Desktop/my.cpgi.file5.txt")
```

#### Exercise 12

```{r}
rn4refseqFilePath = system.file("extdata", "rn4.refseq.bed", package="compGenomRData")
rn4refseq2FilePath = system.file("extdata", "rn4.refseq2name.txt", package="compGenomRData")

df1 = read.table(rn4refseqFilePath, header=FALSE, sep="\t")
df2 = read.table(rn4refseq2FilePath, header=FALSE, sep="\t")
```

#### Exercise 13

```{r}
head(df1)
head(df2)
```

#### Exercise 14

```{r}
new.df = merge(df1, df2)
head(new.df)
```



## Plotting in R

```{r}
set.seed(1001)
x1 = 1:100 + rnorm(100, mean=0, sd=15)
y1 = 1:100
```

#### Exercise 1

```{r}
plot(x1, y1)
```

#### Exercise 2

```{r}
plot(x1, y1, main="Scatter Plot")
```

#### Exercise 3

```{r}
plot(x1, y1, xlab="X Axis Title", ylab="Y Axis Title")
```

#### Exercise 4

```{r}
plot(x1, y1)
mtext(side=3,text="hi there")
```

#### Exercise 5

```{r}
plot(x1, y1)
mtext(side=2,text="hi there")
```

#### Exercise 6

```{r}
plot(x1, y1)
mtext(side=3,text=paste("hi", "there"))
```

#### Exercise 7

```{r}
cor(x1, y1)
```

#### Exercise 8

```{r}
plot(x1, y1)
mtext(side=3,text=paste("The Correlation Coefficient is:", cor(x1, y1)))
```

#### Exercise 9

```{r}
plot(x1, y1, col="red")
```

#### Exercise 10

```{r}
plot(x1, y1, pch=19)
```

#### Exercise 11

```{r}
plot(x1, y1, pch=18)
```

#### Exercise 12

```{r}
hist(x1)
```

#### Exercise 13

```{r}
hist(x1, col="red", xlab="X Axis Title", ylab="Y Axis Title", main="Histogram Title")
```

#### Exercise 14

```{r}
boxplot(y1)
```

#### Exercise 15

```{r}
boxplot(x1, y1)
```

#### Exercise 16

```{r}
boxplot(x1, y1, horizontal=TRUE)
```

#### Exercise 17

```{r}
par(mfrow=c(2, 1))
boxplot(x1, y1)
hist(x1)
```

#### Exercise 18

```{r}
par(mfrow=c(1, 2))
boxplot(x1, y1)
hist(x1)
```

#### Exercise 20

```{r}
x2=1:1000+rnorm(1000,mean=0,sd=200)
y2=1:1000
smoothScatter(x2, y2, colramp=colorRampPalette(c("white","blue", "green","yellow","red")))
```



## Functions and control structures (for, if/else, etc.)

```{r}
cpgtFilePath=system.file("extdata", "CpGi.table.hg18.txt", package="compGenomRData")
cpgi=read.table(cpgtFilePath, header=TRUE, sep="\t")
head(cpgi)
```

#### Exercise 1

```{r}
hist(cpgi$perGc)
```

#### Exercise 2

```{r}
boxplot(cpgi$perGc)
```

#### Exercise 3

```{r}
GCper=65

# check if GC value is lower than 60,
# assign "low" to result
if (GCper < 60) {
  result="low"
  cat("low")
} else if (GCper > 75) { # check if GC value is higher than 75, assign "high" to result
  result="high"
  cat("high")
} else { # if those two conditions fail then it must be "medium"
  result="medium"
}

print(result)
```

#### Exercise 4

```{r}
GCclass <- function (my.gc) {
  # check if GC value is lower than 60,
  # assign "low" to result
  if (my.gc < 60) {
    result="low"
    cat("low")
  } else if (my.gc > 75) { # check if GC value is higher than 75, assign "high" to result
    result="high"
    cat("high")
  } else { # if those two conditions fail then it must be "medium"
    result="medium"
  }
  return(result)
}

GCclass(10) # should return "low"
GCclass(90) # should return "high"
GCclass(65) # should return "medium"
```

#### Exercise 5

```{r}
gcValues = c(10,50,70,65,90)
for(i in gcValues) {
  print(GCclass(i))
}
```

#### Exercise 6

```{r}
lapply(gcValues,GCclass)
```

#### Exercise 7

```{r}
sapply(gcValues,GCclass)
```
