---
title: "Exercise 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

For these exercises, we will be using the following dataset:

```{r}
if (!require("downloader")) {
  install.packages("downloader")
}
library(downloader)
url <- "https://raw.githubusercontent.com/genomicsclass/dagdata/master/inst/extdata/mice_pheno.csv"
filename <- basename(url)
download(url, destfile=filename)
dat <- read.csv(filename)
```

We will remove the lines that contain missing values:

```{r}
dat <- na.omit(dat)
```

## *Question 1*

Use `dplyr` to create a vector x with the body weight of all males on the control (chow) diet. What is this population’s average?

**Answer 1**

```{r}
if (!require("dplyr")) {
  install.packages("dplyr")
}
library(dplyr)
male_control = filter(dat, Diet=="chow", Sex=="M") %>% select(Bodyweight) %>% unlist
mean(male_control)
```

## *Question 2*

Now use the rafalib package and use the popsd function to compute the population standard deviation.

**Answer 2**

```{r}
if (!require("rafalib")) {
  install.packages("rafalib")
}
library(rafalib)
popsd(male_control)
```

## *Question 3*

**Answer 3**

```{r}
male_treatment = filter(dat, Diet=="hf", Sex=="M") %>% select(Bodyweight) %>% unlist
mean(male_treatment)
```

## *Question 4*

Now use the rafalib package and use the popsd function to compute the population standard deviation.

**Answer 4**

```{r}
popsd(male_treatment)
```

## *Question 5*

Calculate the means and variances of the rows of the following simulated data set, and plot the distributions of means and variances using `hist()` and `boxplot()` functions.
```{r}
set.seed(100)

#sample data matrix from normal distribution
gset=rnorm(600,mean=200,sd=70)
data=matrix(gset,ncol=6)
```

**Answer 5**

```{r}
if (!require("matrixStats")) {
  install.packages("matrixStats")
}
library(matrixStats)
row_means = rowMeans(data)
row_vars = rowVars(data)

par(mfrow=c(1, 2))
hist(row_means, main="Distribution of Means")
boxplot(row_means)

par(mfrow=c(1, 2))
hist(row_vars, main="Distribution of Variances")
boxplot(row_vars)
```